### 2018-07-18 99_Documentation/MANUAL/11_StabFem_BasicFunctionalities.tex

\begin{figure*}[t]
\small
\lstinputlisting{../EXAMPLE_Lshape/SCRIPT_Lshape.m}
 \normalsize
\caption{
Matlab program \keys{SCRIPT\_Lshape.m})}
\label{SCRIPT_Lshape.m}
\end{figure*}

\begin{figure*}[t]
\includegraphics[width = .45 \linewidth]{../EXAMPLE_Lshape/FIGURES/Lshape_T0.png}
\includegraphics[width = .45 \linewidth]{../EXAMPLE_Lshape/FIGURES/Lshape_T0_Cut.png}
\caption{Solution for the steady hrat equation in a L-shape domain : $(a)$ Temperature field $T(x,y)$. 
$(b)$ Temperature $T(x,0.25)$ along a horizontal line. }
\label{Lshape_Figures}
\end{figure*}

\begin{figure*}[t]
\small
\lstinputlisting{../EXAMPLE_Lshape/Lshape_Mesh.edp}
 \normalsize
\caption{
FreeFem++ program \keys{Lshape\_Mesh.edp})}
\label{Lshape_Mesh.edp}
\end{figure*}

\begin{figure*}[t]
\small
\lstinputlisting{../EXAMPLE_Lshape/Lshape_Steady.edp}
\normalsize
\caption{
FreeFem++ program \keys{Lshape\_Steady.edp})}
\label{Lshape_Mesh.edp}
\end{figure*}

@@

Looking inside the file \keys{Data.ff2m}, the header (i.e.  first four lines) is as follows :
\lstinputlisting[linerange={1-4}]{../EXAMPLE_Lshape/Data.ff2m}, 
meaning that this files contains a P1 mesh-organised field called 'T'.

@@

Here, besides the file Data.edp previously imported, our program has generated a second data file called \keys{Heat\_1Dcut.ff2m}.
%This file is the one created by the FreeFem program in lines 14-22 of the Freefem program \ref{Lshape_Steady.edp}.
The header of this file is as follows :
\lstinputlisting[linerange={1-5}]{../EXAMPLE_Lshape/Heat_1Dcut.ff2m}, 
meaning that this files contains two vectors of dimension 101 called X and T.

@@

%\lstinputlisting[linerange={1-5}]{../EXAMPLE_Lshape/Heat_1Dcut.ff2m}

%\lstinputlisting{../EXAMPLE_Lshape/ExecutionExample}

>>>>

\begin{figure*}[t]
\small
\lstinputlisting{../../CASES_STABLE/EXAMPLE_Lshape/SCRIPT_Lshape.m}
 \normalsize
\caption{
Matlab program \keys{SCRIPT\_Lshape.m})}
\label{SCRIPT_Lshape.m}
\end{figure*}

\begin{figure*}[t]
\includegraphics[width = .45 \linewidth]{../../CASES_STABLE/EXAMPLE_Lshape/FIGURES/Lshape_T0.png}
\includegraphics[width = .45 \linewidth]{../../CASES_STABLE/EXAMPLE_Lshape/FIGURES/Lshape_T0_Cut.png}
\caption{Solution for the steady hrat equation in a L-shape domain : $(a)$ Temperature field $T(x,y)$. 
$(b)$ Temperature $T(x,0.25)$ along a horizontal line. }
\label{Lshape_Figures}
\end{figure*}

\begin{figure*}[t]
\small
\lstinputlisting{../../CASES_STABLE/EXAMPLE_Lshape/Lshape_Mesh.edp}
 \normalsize
\caption{
FreeFem++ program \keys{Lshape\_Mesh.edp})}
\label{Lshape_Mesh.edp}
\end{figure*}

\begin{figure*}[t]
\small
\lstinputlisting{../../CASES_STABLE/EXAMPLE_Lshape/Lshape_Steady.edp}
\normalsize
\caption{
FreeFem++ program \keys{Lshape\_Steady.edp})}
\label{Lshape_Mesh.edp}
\end{figure*}

@@

Looking inside the file \keys{Data.ff2m}, the header (i.e.  first four lines) is as follows :
\lstinputlisting[linerange={1-4}]{../../CASES_STABLE/EXAMPLE_Lshape/Data.ff2m}, 
meaning that this files contains a P1 mesh-organised field called 'T'.

@@

Here, besides the file Data.edp previously imported, our program has generated a second data file called \keys{Heat\_1Dcut.ff2m}.
%This file is the one created by the FreeFem program in lines 14-22 of the Freefem program \ref{Lshape_Steady.edp}.
The header of this file is as follows :
\lstinputlisting[linerange={1-5}]{../../CASES_STABLE/EXAMPLE_Lshape/Heat_1Dcut.ff2m}, 
meaning that this files contains two vectors of dimension 101 called X and T.

@@

%\lstinputlisting[linerange={1-5}]{../../CASES_STABLE/EXAMPLE_Lshape/Heat_1Dcut.ff2m}

%\lstinputlisting{../../CASES_STABLE/EXAMPLE_Lshape/ExecutionExample}

### 2018-07-18 99_Documentation/MANUAL/211_StabFem_RotatingPolygons.tex

\begin{figure}
\includegraphics[width=.8\linewidth]{../ROTATING_POLYGONS/FIGURES/POLYGONS_modes.png}
\caption{Oscillation modes of a potential vortex for  $a=H/R=0.3$ and $m=3$ (figure 5, 6 of Mougel et al.).}
\label{Bridges_NV_Eigenmodes_phi_cyl_L3_5}
\end{figure}

\begin{figure}
\includegraphics[width=.45\linewidth]{../ROTATING_POLYGONS/FIGURES/POLYGONS_omega.png}
\includegraphics[width=.45\linewidth]{../ROTATING_POLYGONS/FIGURES/POLYGONS_sigma.png}
\caption{Oscillation frequencies and amplification rates for f a potential vortex for $m=3$ (figure 4 of Mougel et al.).}
\label{Bridges_NV_Eigenmodes_phi_cyl_L3_5}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=.8\linewidth]{../../CASES_STABLE/ROTATING_POLYGONS/FIGURES/POLYGONS_modes.png}
\caption{Oscillation modes of a potential vortex for  $a=H/R=0.3$ and $m=3$ (figure 5, 6 of Mougel et al.).}
\label{Bridges_NV_Eigenmodes_phi_cyl_L3_5}
\end{figure}

\begin{figure}
\includegraphics[width=.45\linewidth]{../../CASES_STABLE/ROTATING_POLYGONS/FIGURES/POLYGONS_omega.png}
\includegraphics[width=.45\linewidth]{../../CASES_STABLE/ROTATING_POLYGONS/FIGURES/POLYGONS_sigma.png}
\caption{Oscillation frequencies and amplification rates for f a potential vortex for $m=3$ (figure 4 of Mougel et al.).}
\label{Bridges_NV_Eigenmodes_phi_cyl_L3_5}
\end{figure}
